The Hydrogen Epoch of Reionization Array Dish: Characterization with Electromagnetic Simulations

### 2016-01-13 DishSimulations/paper/DishSimulationsPaper_v1.tex
added clarifictation on the central lobe of Fig 9. in the Dish Simulations paper

\begin{figure}[h!]
\includegraphics[width=.5\textwidth]{figures/powerKernelSubbands.pdf}
\caption{The power kernel for the three subbands discussed in in \S~\ref{ssec:Subbands} along with the kernel for the full bandwidth response function. While the long term falloff from reflections is prominent between $130-160$\,MHz, it appears at a much lower level in the other two subbands which fall below the central subband by $\sim 20$\,dB at $\sim 300$\,ns. $k_\parallel$ values for each delay are computed at $150$\,MHz.}
\label{fig:KernelsSubbands}
\end{figure}

@@

Computing the power spectrum, we inspect

>>>>

\begin{figure}[h!]
\includegraphics[width=.5\textwidth]{figures/powerKernelSubbands.pdf}
\caption{The power kernel for the three subbands discussed in in \S~\ref{ssec:Subbands} along with the kernel for the full bandwidth response function. While the long term falloff from reflections is prominent between $130-160$\,MHz, it appears at a much lower level in the other two subbands which fall below the central subband by $\sim 20$\,dB at $\sim 300$\,ns. $k_\parallel$ values for each delay are computed at $150$\,MHz. The wider central lobe below 150\,ns for the subband gains is an artifact of the delay resolution of a smaller bandwidth.}
\label{fig:KernelsSubbands}
\end{figure}

@@

Computing the power spectra, we inspect the amplitude of foregrounds given the chromaticity and angular pattern of the HERA dish for several different baselines of different lengths.
